### 2023-11-25 Paper/main.tex
Fix image path and update training details

\begin{figure}[h!]
    \centering
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{psnr.png}
          \caption{PSNR comparison of the used codecs}
          \label{fig: psnr_comparison}
      \end{subfigure}
      \hfill
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{ssim.png}
          \caption{SSIM comparison of the used codecs}
          \label{fig:CI}
      \end{subfigure}
\caption{
\label{fig: comparison}%
Comparison of PSNR and SSIM}
\end{figure}

@@

The idea behind training the network from scratch is that the network would be more tailored to the given task since it has no previous information stored in the network. This contrasts with transfer learning since there prior information is present.
\newline

@@

\noindent
To train the network the DIV2K training and validation dataset was used. The dataset contains 800 train images and 100 test images. Since the images had different dimensions, we first had to crop them to specific in this case 512x512. Afterwards we compressed the images to specified file sizes as described in \ref{sec: filesize}. This leads to 10 classes – one for each compression algorithm – for each file size category. We trained the network by using the images that were compressed to a file size of 25kB.
\newline

@@

\noindent
After 10 epochs of training, we achieved a validation accuracy of 57,6 percent. For 10 epochs this is lower than the results we got for the transfer learning approach. However, if one would increase the number of epochs, we expect to reach the same levels of accuracy since the only defencemen is that the pretrained network has a preferable starting position compared to the one without transfer learning. This can be shown by changing the starting seed to something different leading to only 10 percent accuracy after 10 epochs.

\subsection{Transferlearning}
For this approach the ResNet18 model was used as a baseline. To adjust this pretrained model for the requirements of the experiment, the output layers where reconfigured to represent the 8 different codecs in which the images where encoded.
In addition the model uses just 224x224 images as inputs, thus the encoded images where center cropped to fit that size.

@@

\noindent
The self trained model showed an accuracy over all filesizes of 10 percent. With ten different codecs, random guessing would lead to the same result as this model. For the self trained model 40000 images where used. The pretrained model was already trained on 1,2 million images. Therefore, the self trained model would need much more images to get a better performance. With only 2400 images used for training, this model represents the worst model for the classification task.

>>>>

\begin{figure}[h!]
    \centering
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{psnr.png}
          \caption{PSNR comparison of the used codecs}
          \label{fig: psnr_comparison}
      \end{subfigure}
      \hfill
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../Plots/ssim.png}
          \caption{SSIM comparison of the used codecs}
          \label{fig:CI}
      \end{subfigure}
\caption{
\label{fig: comparison}%
Comparison of PSNR and SSIM}
\end{figure}

@@

The idea behind training the network from scratch is that the network would be more tailored to the given task since it has no previous information stored in the network. This contrasts with transfer learning since there prior information is present. As a model the ResNet18 architecture was used. This architecture was chosen since it is a good compromise between network size and performance.
\newline

@@

\noindent
To train the network the DIV2K training and validation dataset was used. The dataset contains 800 train images and 100 test images. Since the images had different dimensions, we first had to crop them to specific in this case 512x512. Afterwards we compressed the images to specified file sizes as described in \ref{sec: filesize}. With the primary objectice beeing to recignize the different compression algorithms the output of the network should represent the different encoding schemes. This leads to 10 classes in each file size category.

@@

\noindent
After 10 epochs of training, we achieved a validation accuracy of 57,6 percent avaged over the 5 training filesizes (5, 10, 17, 25 and 32). For 10 epochs this is lower than the results we got for the transfer learning approach. However, if one would increase the number of epochs, we expect to reach the same levels of accuracy since the only defencemen is that the pretrained network has a preferable starting position compared to the one without transfer learning. This can be shown by changing the starting seed to something different leading to only 10 percent accuracy after 10 epochs.

\subsection{Transferlearning}
To be able to compare the results of the self-trained model with a pretrained model, the ResNet18 architecture was used again. The pretrained model was already trained on 1,2 million images to give an preferable starting position for training. To adjust this pretrained model for the requirements of the experiment, the output layers where reconfigured to represent the 10 different codecs in which the images where encoded.
In addition the model uses just 224x224 images as inputs, thus the encoded images where center cropped to fit that size.

@@

\noindent
The self trained model was trained with the filesizes 5, 10, 17, 25 and 32 on all 10 codecs. This leads to 4000 images for each codec per epoch. As one can see in figure \ref{fig: acc_comparison} the self trained model has its best performances at filesizes 10, 17 and 25 ranging from 62 to 65 percent accuracy.
